### 2017-08-30 paper.tex
:hammer: Fix reference style

%\documentclass{tuhhproc-en}
\documentclass[12pt,twoside]{tuhhproc-en}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times,rotating}
\usepackage[round, sort, numbers, authoryear]{natbib} %author year

@@

\begin{document}

@@

\section{Introduction}

Catastrophic earth movement events, such as landslides, debris flows, rock avalanches and reservoir embankment failures, exemplify the potential consequences of an earth gravitational instability. Slope failure is a problem of high practical importance for both civil engineering structures and natural hazard management. The study described in this paper examines the stability of underwater slopes, which are caused by excess seepage or earthquakes.  They can damage offshore structures nearby and may generate a tsunami.

@@

\selectlanguage{english}
\bibliographystyle{apalike}
\bibliography{references} % Path to your References.bib file

>>>>

%\documentclass{tuhhproc-en}
\documentclass[12pt,twoside]{tuhhproc-en}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times,rotating}

\usepackage[backend=biber, style=numeric, citestyle=authoryear, sorting=nty, natbib=true]{biblatex}
\bibliography{references} %Location of references.bib only for biblatex

@@

\begin{document}
\selectlanguage{english}

@@

\section{Introduction}
Catastrophic earth movement events, such as landslides, debris flows, rock avalanches and reservoir embankment failures, exemplify the potential consequences of an earth gravitational instability. Slope failure is a problem of high practical importance for both civil engineering structures and natural hazard management. The study described in this paper examines the stability of underwater slopes, which are caused by excess seepage or earthquakes.  They can damage offshore structures nearby and may generate a tsunami.

@@

\selectlanguage{english}
\section*{References}
\printbibliography[heading=none]
